%!TEX TS-program = xelatex
\documentclass[]{cv}

\begin{document}
\header{j}{robert}{wells}
       {software developer}

% In the aside, each new line forces a line break
\begin{aside}
  \section{about}
    {Portland, OR}
    \href{http://jrobertwells.com}{jrobertwells.com}
    ~
    (512) 922-3599
    \href{mailto:jrwells10@gmail.com}{jrwells10@gmail.com}
    \href{http://github.com/jrwells}{github.com/jrwells}
    \href{https://twitter.com/jrobwells}{twitter.com/jrobwells}
  \section{programming}
    Python, JavaScript
    HTML/CSS, Nim
    Java, C#, Ruby
  \section{software}
    Git, SVN, Mercurial
    Xcode, Eclipse
    Visual Studio
    Adobe Creative Suite
    Rhino & Grasshopper
\end{aside}

\section{interests}

computational geometry, computer-aided design & engineering, computer simulation, \\
machine learning, pattern recognition, artificial intelligence, \\
web application development, aerospace engineering, organizational design

\section{work experience}

\begin{entrylist}
  \entry
    {2016-Present}
    {Mode Lab - Portland, OR}
    {Software Engineer}
    {\emph{Designing and building custom CAD/CAE applications & tools that solve client specific problems, ranging from product design to manufacturing.}}
  \entry
    {05-08, 2015}
    {Undercurrent - New York, NY}
    {Full Stack Developer}
    {\emph{Built Ruby and Node API interfaces for HolacracyOne's GlassFrog platform and designed software for ever better organizations.}}
  \entry
    {06-08, 2013}
    {Caringo Inc - Austin, TX}
    {Software Development Intern}
    {\emph{Designed and implemented the server-side of an HTTP communication platform using Python.}}
  \entry
    {08-12, 2012}
    {Washington University - St. Louis, MO}
    {Teaching Assistant}
    {\emph{Instructed students in lab and graded assignments for CSE 131, an introductory computer science course.}}
  \entry
    {06-08, 2011}
    {Selenium LTD - Austin, TX}
    {Lab Intern}
    {\emph{Worked on the development of a chemiluminescence test for their selenium coating technology.}}
  \entry
    {06-08, 2010}
    {ESO Solutions - Austin, TX}
    {Quality Assurance Intern}
    {\emph{Tested software which helps emergency first-responders connect more rapidly to hospitals.}}
\end{entrylist}

\section{education}

\begin{entrylist}
  \entry
    {2010–2014}
    {B.S. in Computer Science}
    {Washington University in St. Louis, St. Louis, MO}
    {\emph{Topics included: Object‐Oriented Software Development, Systems Software, Rapid Prototype Development, and Creative Programming.}}
  \entry
    {2006-2010}
    {High School}
    {St. Stephen’s Episcopal School, Austin, TX}
    {\emph{Topics included: Advanced Biology, Advanced Physics, Astrophysics, Calculus, Chemistry, Latin, and Robotics.}}
\end{entrylist}

\section{academic experiences}

\begin{entrylist}
  \entry
    {2009}
    {Purdue University STEP Engineering Program}{}
    {\emph{Introduction to biomedical and mechanical engineering.}}
  \entry
    {2008-2009}
    {People to People Ambassador Program}{}
    {\emph{Traveled to China for 2 weeks, after 8 months of preparatory study. Stayed with a local family and did community service.}}
  \entry
    {2008}
    {Worcester Polytechnic Institute Frontiers Program}{}
    {\emph{Computer science and music program. Studies included: JavaScript, CGI, StarLogo, Pearl and Python.}}
\end{entrylist}

\end{document}
